
#Install packages to try running stuff

```{r}
library(TrenchR)
```
#' @title Operative Environmental Temperature of a Mussel
#' 
#' @description The function estimates body temperature (C, operative environmental temperature) of a mussel. The function implements a steady-state model, which assumes unchanging environmental conditions. 
#' 
#' @param l \code{numeric} mussel length (anterior/posterior axis, m).
#' 
#' @param h \code{numeric} mussel height (dorsal/ventral axis, m). It is reasonable to assume \code{h = 0.5 * l}.
#' 
#' @param T_a \code{numeric} air temperature (C).
#' 
#' @param T_g \code{numeric} ground temperature (C).
#' 
#' @param S \code{numeric} direct solar flux density (\ifelse{html}{\out{W m<sup>-2</sup>}}{\eqn{W m^-2}{ASCII}}).
#' 
#' @param k_d \code{numeric} diffuse fraction, proportion of solar radiation that is diffuse.
#' 
#' @param u \code{numeric} wind speed (\ifelse{html}{\out{m s<sup>-1</sup>}}{\eqn{m s^-1}{ASCII}}).
#' 
#' @param psi \code{numeric} solar zenith angle (degrees): can be calculated from \code{\link{zenith_angle}}.
#' 
#' @param evap \code{logical} Whether mussel is gaping to evaporatively cool. If \code{TRUE}, the function assumes a constant mass loss rate of 5 percent of the initial body mass per hour. 
#' 
#' @param cl \code{numeric} fraction of the sky covered by cloud. 
#' 
#' @param group \code{character}; options are \code{"aggregated"}: mussels living in beds; \code{"solitary"}: solitary individual, anterior or posterior end facing upwind; and \code{"solitary_valve"}: solitary individual, valve facing upwind.
#'
#' @details Thermal radiative flux is calculated following \insertCite{Helmuth1998;textual}{TrenchR}, \insertCite{Helmuth1999;textual}{TrenchR}, and \insertCite{Idso1969;textual}{TrenchR}.
#'
#' @return \code{numeric} predicted body (operative environmental) temperature (C).
#' 
#' @family biophysical models
#' 
#' @references
#'  \insertAllCited{}
#'
#' @export
#' 
#' @examples
#' 
#' Tb_mussel(l     = 0.1, 
#'           h     = 0.05, 
#'           T_a   = 25, 
#'           T_g   = 30, 
#'           S     = 500, 
#'           k_d   = 0.2, 
#'           u     = 2, 
#'           psi   = 30, 
#'           evap  = FALSE, 
#'           cl    = 0.5, 
#'           group = "solitary")
#' 



# Messing around with mussel stuff
```{r}

```

